### 2019-12-04 thesis.tex
Final (I promise)

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, which, for $a=e$, is given by
\begin{equation}
  \begin{split}
    \sum_b\theta_{eb}(\Phi_e,\Phi_b) &= \sum_b \Gamma_{eb}
    \left\{\frac{\partial}{\partial{\bf u}}\cdot
     \left(2\frac{m_e}{m_b}\Psi(u_{eb})
     \frac{{\bf u}}{u^3}\Phi_e\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}}\cdot
     \left\{\left[\left(\Phi(u_{eb})
     -\frac{1}{2 u_{eb}^2}\Psi(u_{eb})\right)
     \frac{\partial^2u}{\partial{\bf u}
     \partial{\bf u}}\right]\cdot
     \frac{\partial \Phi_e}{\partial{\bf u}}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}}\cdot
     \left[\left(\frac{1}{u_{eb}^2}\Psi(u_{eb})
     \frac{{\bf u}{\bf u}}{u^3}\right)\cdot
   \frac{\partial \Phi_e}{\partial{\bf u}}\right]\right\},
\end{split}
\end{equation}
where $u_{eb}\equiv u (v_{t_e}/v_{t_b})$, $u=v/v_{t_e}$,
with $v_{t_e}$ and $v_{t_b}$ representing the thermal velocity of
electrons and thermal velocity of the particles of species $b$,
with $b=e,i$. The quantity $\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an
auxiliary function \cite{Gaffey1976}, in which
$\Phi(x) \equiv \frac{2}{\sqrt{\pi}}\int_0^x e^{-t^2}dt$ is the error
function and $\Phi'(x)=\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative.
The factor $\Gamma_{eb}$ is given by $\Gamma_{eb}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the charge number of ions and electrons, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray*}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray*}

@@

\begin{appendix}
\chapter{Improved approximation for the second order susceptibility}
\label{appA}
\setcounter{equation}{0}
\renewcommand{\theequation}{A\arabic{equation}}
In this appendix, we present two different approximations applied to the
second-order susceptibility in the electrostatic bremsstrahlung equation
for Langmuir waves. Initially, for comparison, we show the original
simplification used in Ref.~\cite{YZKS16}. In the sequence, we introduce
an improved approximation for the same expression, highlighting the main
differences. This new version, though, is only suitable for fast-waves,
which is the case of Langmuir oscillations, but does not apply to the case
% LFZ190822: Aqui me parece que ficaria melhor dizer This new version, though,
% is only suitable for fast waves, which is the case of Langmuir oscillations,
% but does not apply to the case of ion-sound waves. does not apply
% Sabrina: ok
of ion-sound waves. Moreover, the results for ion-sound waves are quite
well behaved with the original approximation, which is the same that was
initially used for $L$ waves in Ref.~\cite{YZKS16}.
% LFZ190822: Acho que aqui cabe continuar dizendo "... for $L$ waves in
% Ref.~\cite{YZKS16}."
% Sabrina: ok
Therefore, $S$ waves will be considered only in
% LFZ190822: Acho melhor "will be considered", em vez de "will take part"
\Cref{sec:orig-appr}, while \Cref{sec:alt-approx} will be directed solely
% LFZ190822: Sugiro "... will be directed solely to the use in expressions
% related to $L$ waves.", em lugar de "the $L$ waves expression."
% Sabrina: acho que se eu usar "expressions" vai dar a impressão de que
% essa aproximação vai ser usada em outra equação que não seja a do
% electrostatic bremsstrahlung. Não lembro se a gente chegou a usar essa
% aproximação na expressão do amortecimento colisional. Mas acho que não.
to the  expression for $L$ waves.

@@

\chapter{Asymptotic equilibrium}
\label{appB}
The results presented in Ref. \cite{Tigik2017a} suggest that in the presence
of electrostatic bremsstrahlung emission, the wave-particle system evolves to
a state of asymptotic equilibrium, in which the velocity distribution resembles
the ubiquitous core-halo velocity distribution. To test this assumption, we
search for the steady state solution of the kinetic equation for Langmuir waves,
taking into account the effects of collisional damping and electrostatic
bremsstrahlung, in addition to the spontaneous and induced emission processes,
\begin{equation}
  \frac{\partial {\cal E}_{\bf q}^{\sigma L}}
  {\partial \tau}
  =\mu_{\bf q}^L\frac{\pi}{q^2}
  \int d{\bf u}\;\delta(\sigma
  z_{\bf q}^L-{\bf q}\cdot{\bf u})\biggl(g\,\Phi_e({\bf u})
  +\sigma z_{\bf q}^L\,{\cal E}_{\bf q}^{\sigma L}
  \,{\bf q}\cdot\frac{\partial \Phi_e}{\partial{\bf u}}\biggr)
  +P_{\bf q}^{\sigma L}+2\gamma_{\bf q}^{\sigma L}{\cal E}_{\bf q}^{\sigma L}\approx 0,
  \label{asymp}
\end{equation}

@@

Proceeding in the same way, the expression at the denominator
of the expression for the asymptotic wave spectrum becomes
\begin{equation*}
  \begin{split}
   \left(1-\frac{n_{\kappa e}}{n_e}\right)
  &\frac{1}{\pi^{1/2} u_{e}}\frac{1}{q}
  \exp\left(-\frac{(z_q^L/q)^2}{u_{e}^2}\right)
  +\frac{u_e^2}{u_{e,\kappa}^2}
  \frac{n_{\kappa e}}{n_e}
  \frac{1}{\pi^{1/2} \kappa_e^{1/2} u_{e,\kappa}}\\
  &\times\frac{\Gamma(\kappa_e)}{\Gamma(\kappa_e-1/2)}
  \frac{1}{q}\left(1+\frac{(z_q^L/q)^2}{\kappa_e u_{e,\kappa}^2}
  \right)^{-(\kappa_e+1)}
  -\frac{1}{\mu_{\bf q}^L}\frac{q^2}{\pi}
  \frac{T_e}{T_*}\frac{1}{(\sigma z_q^L)^2}
  \gamma_{\bf q}^{\sigma L(coll)}.
 \end{split}
\end{equation*}

>>>>

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, which, for $a=e$, is given by
\begin{equation}
  \begin{split}
    \sum_b\theta_{eb}(\Phi_e,\Phi_b) &= \sum_b \Gamma_{eb}
    \left\{\frac{\partial}{\partial{\bf u}}\cdot
     \left(2\frac{m_e}{m_b}\Psi(u_{eb})
     \frac{{\bf u}}{u^3}\Phi_e\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}}\cdot
     \left\{\left[\left(\Phi(u_{eb})
     -\frac{1}{2 u_{eb}^2}\Psi(u_{eb})\right)
     \frac{\partial^2u}{\partial{\bf u}
     \partial{\bf u}}\right]\cdot
     \frac{\partial \Phi_e}{\partial{\bf u}}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}}\cdot
     \left[\left(\frac{1}{u_{eb}^2}\Psi(u_{eb})
     \frac{{\bf u}{\bf u}}{u^3}\right)\cdot
   \frac{\partial \Phi_e}{\partial{\bf u}}\right]\right\},
\end{split}
\end{equation}
where $u_{eb}\equiv u (v_{t_e}/v_{t_b})$, $u=v/v_{t_e}$,
with $v_{t_e}$ and $v_{t_b}$ representing the thermal velocity of
electrons and thermal velocity of the particles of species $b$,
with $b=e,i$. The quantity $\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an
auxiliary function \cite{Gaffey1976}, in which
$\Phi(x) \equiv \frac{2}{\sqrt{\pi}}\int_0^x e^{-t^2}dt$ is the error
function and $\Phi'(x)=\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative.
The factor $\Gamma_{eb}$ is given by $\Gamma_{eb}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the charge number of ions and electrons, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray}

@@

\begin{appendix}
\chapter{Improved approximation for the second order susceptibility}
\label{appA}
\setcounter{equation}{0}
\renewcommand{\theequation}{A.\arabic{equation}}
In this appendix, we present two different approximations applied to the
second-order susceptibility in the electrostatic bremsstrahlung equation
for Langmuir waves. Initially, for comparison, we show the original
simplification used in Ref.~\cite{YZKS16}. In the sequence, we introduce
an improved approximation for the same expression, highlighting the main
differences. This new version, though, is only suitable for fast-waves,
which is the case of Langmuir oscillations, but does not apply to the case
% LFZ190822: Aqui me parece que ficaria melhor dizer This new version, though,
% is only suitable for fast waves, which is the case of Langmuir oscillations,
% but does not apply to the case of ion-sound waves. does not apply
% Sabrina: ok
of ion-sound waves. Moreover, the results for ion-sound waves are quite
well behaved with the original approximation, which is the same that was
initially used for $L$ waves in Ref.~\cite{YZKS16}.
% LFZ190822: Acho que aqui cabe continuar dizendo "... for $L$ waves in
% Ref.~\cite{YZKS16}."
% Sabrina: ok
Therefore, $S$ waves will be considered only in
% LFZ190822: Acho melhor "will be considered", em vez de "will take part"
\Cref{sec:orig-appr}, while \Cref{sec:alt-approx} will be directed solely
% LFZ190822: Sugiro "... will be directed solely to the use in expressions
% related to $L$ waves.", em lugar de "the $L$ waves expression."
% Sabrina: acho que se eu usar "expressions" vai dar a impressão de que
% essa aproximação vai ser usada em outra equação que não seja a do
% electrostatic bremsstrahlung. Não lembro se a gente chegou a usar essa
% aproximação na expressão do amortecimento colisional. Mas acho que não.
to the  expression for $L$ waves.

@@

\chapter{Asymptotic equilibrium}
\label{appB}
\setcounter{equation}{0}
\renewcommand{\theequation}{B.\arabic{equation}}
The results presented in Ref. \cite{Tigik2017a} suggest that in the presence
of electrostatic bremsstrahlung emission, the wave-particle system evolves to
a state of asymptotic equilibrium, in which the velocity distribution resembles
the ubiquitous core-halo velocity distribution. To test this assumption, we
search for the steady state solution of the kinetic equation for Langmuir waves,
taking into account the effects of collisional damping and electrostatic
bremsstrahlung, in addition to the spontaneous and induced emission processes,
\begin{equation}
  \frac{\partial {\cal E}_{\bf q}^{\sigma L}}
  {\partial \tau}
  =\mu_{\bf q}^L\frac{\pi}{q^2}
  \int d{\bf u}\;\delta(\sigma
  z_{\bf q}^L-{\bf q}\cdot{\bf u})\biggl(g\,\Phi_e({\bf u})
  +\sigma z_{\bf q}^L\,{\cal E}_{\bf q}^{\sigma L}
  \,{\bf q}\cdot\frac{\partial \Phi_e}{\partial{\bf u}}\biggr)
  +P_{\bf q}^{\sigma L}+2\gamma_{\bf q}^{\sigma L}{\cal E}_{\bf q}^{\sigma L}\approx 0,
  \label{asymp}
\end{equation}

@@

Proceeding in the same way, the expression for the denominator
of the asymptotic wave spectrum becomes
\begin{equation*}
  \begin{split}
   \left(1-\frac{n_{\kappa e}}{n_e}\right)
  &\frac{1}{\pi^{1/2} u_{e}}\frac{1}{q}
  \exp\left(-\frac{(z_q^L/q)^2}{u_{e}^2}\right)
  +\frac{u_e^2}{u_{e,\kappa}^2}
  \frac{n_{\kappa e}}{n_e}
  \frac{1}{\pi^{1/2} \kappa_e^{1/2} u_{e,\kappa}}\\
  &\times\frac{\Gamma(\kappa_e)}{\Gamma(\kappa_e-1/2)}
  \frac{1}{q}\left(1+\frac{(z_q^L/q)^2}{\kappa_e u_{e,\kappa}^2}
  \right)^{-(\kappa_e+1)}
  -\frac{1}{\mu_{\bf q}^L}\frac{q^2}{\pi}
  \frac{T_e}{T_*}\frac{1}{(\sigma z_q^L)^2}
  \gamma_{\bf q}^{\sigma L(coll)}.
 \end{split}
\end{equation*}
